---
title: "Data_Analyses_MGT_Swabian_single_gender"
author: "Judit Vari"
date: "30 7 2024"
output: html_document
---

```{r setup, include=FALSE}
library (dplyr)
library(broom)
library(tidyverse)
library(corrr)
library(ggcorrplot)
library(car)
library(readr)
library(here)
library(ordinal)
library(lmerTest)
library(emmeans)
library(sjPlot)
library(report)
library (afex)
library(lme4)
library(optimx)
library(sjPlot)
library(ggeffects)
library(factoextra)
library(FactoMineR)
```
### Read data & assign classes

```{r setup1, include=FALSE}
result <- read_delim(here("data_processed", "data_clean.csv"), col_names = TRUE, delim = ",")
colnames(result)



as.factor(result$bilendi_id)->result$bilendi_id

as.factor(result$lang.exposure)->result$lang.exposure
as.factor(result$Audio_Track)->result$Audio_Track
as.factor(result$condition)->result$condition
as.factor(result$Speaker)->result$Speaker
as.factor(result$Speaker_Gender)->result$Speaker_Gender
as.factor(result$Attribute)->result$Attribute
as.factor(result$deceived)->result$deceived
as.factor(result$`Political level`)-> result$`Political level`
as.factor(result$Audio_Track_origin_non_st)->result$Audio_Track_origin_non_st
as.factor(result$Audio_Track_origin_st)->result$Audio_Track_origin_st
as.factor(result$Statement_no)-> result$Statement_no
as.factor(result$`identity_lang.variety_non-st`)-> result$`identity_lang.variety_non-st`
as.factor(result$identity_lang.variety_st)-> result$identity_lang.variety_st
as.factor(result$gender)->result$gender
as.factor(result$state_of_residence)->result$state_of_residence
as.factor(result$party)->result$party
as.factor(result$education_school)->result$education_school
as.factor(result$education_profession1)->result$education_profession1
as.factor(result$income)->result$income
as.factor(result$profession)->result$profession
as.factor(result$education_profession1_sum)->result$education_profession1_sum
as.factor(result$education_school_sum)-> result$education_school_sum
as.factor(result$lang.exposure)->result$lang.exposure
as.factor(result$Lang.Variety_Audio)->result$Lang.Variety_Audio




as.numeric(result$Response)->result$Response
as.numeric(result$Att.check_acc)->result$Att.check_acc
as.numeric(result$age)->result$age
as.numeric(result$`proximity_variety_non-st`)->result$`proximity_variety_non-st`
as.numeric(result$proximity_variety_st)->result$proximity_variety_st
as.numeric(result$political_orientation_A)->result$political_orientation_A
as.numeric(result$political_orientation_B)->result$political_orientation_B
as.numeric(result$political_orientation_C)->result$political_orientation_C
as.numeric(result$political_orientation_D)->result$political_orientation_D
as.numeric(result$own_dialect)-> result$own_dialect
as.numeric(result$`social_desirability_A-quantised`)-> result$`social_desirability_A-quantised`
as.numeric(result$`social_desirability_B-quantised`)-> result$`social_desirability_B-quantised`
as.numeric(result$`social_desirability_C-quantised`)-> result$`social_desirability_C-quantised`
as.numeric(result$`social_desirability_D-quantised`)-> result$`social_desirability_D-quantised`
as.numeric(result$`social_desirability_E-quantised`)-> result$`social_desirability_E-quantised`
as.numeric(result$`social_desirability_F-quantised`)-> result$`social_desirability_F-quantised`
as.numeric(result$`social_desirability_G-quantised`)-> result$`social_desirability_G-quantised`
as.numeric(result$`social_desirability_H-quantised`)-> result$`social_desirability_H-quantised`
as.numeric(result$`social_desirability_I-quantised`)-> result$`social_desirability_I-quantised`
as.numeric(result$populism_A)-> result$populism_A
as.numeric(result$populism_B)-> result$populism_B
as.numeric(result$populism_C)-> result$populism_C
as.numeric(result$populism_D)-> result$populism_D
as.numeric(result$political_spectrum)-> result$political_spectrum


```
# scale variables

```{r setup2, include=FALSE}
scale (result$Response)->result$Response
scale(result$political_spectrum)-> result$political_spectrum
scale(result$age)->result$age
scale(result$own_dialect)->result$own_dialect

```
# exclude participants failing attention checks

```{r setup3, include=FALSE}

result%>%
  ggplot(aes(x=Att.check_acc)) +
  ggtitle ("Plot of Attention Check")+
  xlab("accuracy attention check")+
         geom_density()-> plot_attention

result%>%
  filter(Att.check_acc > 85)%>%
  summarise(n_distinct(bilendi_id))-> pp_above_85atten

result%>%
  filter(Att.check_acc > 85)->result

result%>%
  ggplot(aes(x=Att.check_acc)) +
  ggtitle ("Plot of Attention Check")+
  xlab("accuracy attention check")+
         geom_density()-> plot_attention

plot_attention

```
## Create subsets 

### in- and outgroup 
Separate ingroup from outgroup based on exposure to Swabian, outgroup consists of other non-standard, vernacular speakers, standard speakers and bilinguals
Continue with analyses of outgroup data set

### subdived outgroup into two conditions: participants either exposed to only one gender (male or female speaker) or two genders (male vs. female speakers)

```{r setup2, include=FALSE}


result%>%
  filter(lang.exposure != "in-group")-> outgroup

result%>%
  filter(lang.exposure == "in-group")-> ingroup

# check groups

outgroup%>%
  group_by(lang.exposure)%>%
  summarise(n_distinct(bilendi_id))->lang.ex_out

ingroup%>%
   group_by(lang.exposure)%>%
  summarise(n_distinct(bilendi_id))->lang.ex_in

levels(outgroup$condition)
outgroup%>%
  filter (condition== "single_gender")->outgroup_sing

outgroup%>%
  filter (condition== "contrasted_gender")->outgroup_contrast

```
## Plots raw data
plot responses attributes
```{r plot responses attributes}

# Charisma
outgroup_sing%>%
  filter (Attribute == "charismatisch")%>%
ggplot(aes(x=Response)) +
  ggtitle ("Plot of Attribute Charisma")+
  xlab("ratings")+
         geom_density()-> plot_charisma

plot_charisma


outgroup_sing%>%
  drop_na(Lang.Variety_Audio)%>%
filter (Attribute == "charismatisch")%>%
ggplot(aes(y=Response, x=Lang.Variety_Audio))+
geom_boxplot()+
  ggtitle ("Plot of Attribute Charisma")

## all attributes

outgroup_sing%>%
  drop_na(Lang.Variety_Audio)%>%
ggplot(aes(y=Response, x=Attribute))+
geom_boxplot()+
  ggtitle ("Plot of all Attributes")

```

## Prep political background  
####PCA

```{r PCA_populism, echo=FALSE}
outgroup_sing%>%
  ungroup()%>%
  select(bilendi_id, populism_A, populism_B, populism_C, populism_D)-> PCA_pop_data


distinct (PCA_pop_data)-> PCA_pop_data 
pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE, graph = TRUE) # option to include quali & quanti variables


fviz_eig(pca_pop) # scree plot variance explained dimensions, keep 2

pca_pop$var$coord

pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE,
               graph = T, ncp = 2)

summary(pca_pop)

dimdesc(pca_pop, axes = c(1,2))



p_1a <- fviz_pca_var(pca_pop,geom = c("point","text"),
                  label = "var",
                  repel = TRUE,
                  col.var = "contrib",   # colour active variables according to their contribution to PCA axes
                  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
                  title= "PCA populism"
)

p_1a 

#ggsave(here("Output", "outgroup_PCA_populism.jpg"))
```
*dimension reduction populism scales 1-4 after PCA*
```{r PCA_dim_reduction_populism, echo=FALSE}


populism_dim <- pca_pop$ind$coord [,1]

as_tibble(populism_dim)->populism_dim

bind_cols(PCA_pop_data, populism_dim)->PCA_pop_data_final

left_join (outgroup_sing, PCA_pop_data_final, by = c("bilendi_id", "populism_A", "populism_B", "populism_C", "populism_D"))-> outgroup_sing # 
  
rename (outgroup_sing, populism_dim = value)-> outgroup_sing
```
*final dummy variables populism*
create 2 dummy variables for populism a) mean of populism scores items A-C, but exclude pop D -> PCA shows very different b) use principal component 1 as dummy
```{r poplitical bckgr pop_dummies, echo=FALSE}
outgroup_sing %>%
  mutate(populism_all = rowMeans(across(c(populism_A, populism_B, populism_C), as.numeric, .names = "mean_{col}"), na.rm = TRUE)) -> outgroup_sing


outgroup_sing%>%
  distinct(bilendi_id, populism_all)%>%
ggplot(aes(x=populism_all))+
  ggtitle("Plot of Populism Mean Scores") +
         geom_density()+
  ylab("no. of participants")+
  xlab("total score of populism items 1-3")-> Plot_sum_pop1
Plot_sum_pop1
#ggsave(here("Output", "Plot_sum_pop1.jpg"))


# add new populism dimension 1 of PCA
as.numeric(outgroup_sing$populism_dim)-> outgroup_sing$populism_dim

populism_dim%>%
   ggplot(aes(x=value))+
     ggtitle("Plot of Populism Dimension") +
     geom_density()+
  xlab ("Populism Prinincipal Component Scores")-> Plot_sum_pop2
Plot_sum_pop2

```

# Plot polit. backgr

```{r political_bckgr}


outgroup_sing%>%
  ggplot(aes(x=political_spectrum))+
  ggtitle("Plot of Political Spectrum") +
         geom_density()+
  ylab("no. of participants")+
  xlab("from left to right")-> Plot_polt.spec
Plot_polt.spec


```

# RQ 1: Does language variety affect perceived charisma and other traits?
```{r lang.var}
outgroup_sing%>%
  ungroup()%>%
  select(bilendi_id, Response, Attribute, Audio_Track, age, political_spectrum, populism_A, populism_B, populism_C, populism_D, populism_all, own_dialect)-> nummeric

distinct(nummeric)->nummeric

nummeric%>%
  pivot_wider(names_from = Attribute, values_from = Response, id_cols = c("bilendi_id", "Audio_Track", "age", "political_spectrum", "populism_all", "own_dialect"))-> nummeric_long

nummeric_long%>%
distinct()%>%
  select(-bilendi_id, -Audio_Track)%>%
  drop_na()->nummeric_long

nummeric_long %>%
mutate(across(5:10, as.numeric))-> nummeric_long

cor(nummeric_long)->matrix_num_long

matrix_num_long
# Visualize correlations


ggcorrplot(matrix_num_long, 
           title = "Nummeric variables", hc.order = TRUE, 
           type = "lower",lab = TRUE, lab_size = 2.5,  insig = "blank")->plot_corr_matrix
plot_corr_matrix

#ggsave(here ("output", "plot_corr_matrix.jpg"))
```
## Impact language variety main + interaction gender
RQ: Do participants rate speakers of standard language variety more charismatic ompared the vernacular variety?
RQ 2: Does gender moderate an effect of lang. variety?

```{r glm_lang.var_chari, eval=FALSE, include=FALSE}



# only charisma ratings
outgroup_sing%>%
  filter(Attribute=="charismatisch")->outgroup_sing_chari

outgroup_sing_chari$Lang.Variety_Audio = relevel(outgroup_sing_chari$Lang.Variety_Audio, ref = "Regional Variety")

outgroup_sing_chari$gender = relevel(outgroup_sing_chari$gender, ref = "Weiblich")
as.factor(outgroup_sing_chari$bilendi_id)-> outgroup_sing_chari$bilendi_id

colnames(outgroup_sing_chari)

# lmer (Response ~ Lang.Variety_Audio*Speaker_Gender + gender + age + education_school_sum + Polit_ori + (Lang.Variety_Audio*Speaker_Gender|bilendi_id) +  (1|Audio_Track) + (1|Statement_no), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence


#lmer (Response ~ Lang.Variety_Audio*Speaker_Gender + gender + age + education_school_sum + Polit_ori + (Lang.Variety_Audio+Speaker_Gender|bilendi_id) +  (1|Audio_Track) + (Lang.Variety_Audio|Statement_no), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence

# lmer (Response ~ Lang.Variety_Audio*Speaker_Gender + gender + age + education_school_sum + Polit_ori + (Speaker_Gender|bilendi_id) +  (1|Audio_Track) + (Lang.Variety_Audio|Statement_no), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence


 #lmer (Response ~ Lang.Variety_Audio*Speaker_Gender + gender + age + education_school_sum + Polit_ori + (Speaker_Gender|bilendi_id) +  (1|Audio_Track) + (1|Statement_no), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence


lmer (Response ~ Lang.Variety_Audio*Speaker_Gender + gender + age + education_school_sum + political_spectr +  Statement_no + (1|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence

summary(model1a)

anova(model1a)



plot_model(model1a, title = "Predicted values of charisma ratings", type = "pred", terms = c("Lang.Variety_Audio", "Speaker_Gender")) +
  ylab ("Charisma ratings")+
     labs(colour= str_wrap("Speaker Gender", width = 15))->plot_model1a
plot_model1a

```


```{r lang.gender}
```

# RQ 3: Does pop. attitude moderate an effect of lang. variety?
```{r lang.pop}
```
# RQ 4: Does political statment moderate an effect of lang. variety?
```{r lang.pol_stat}

```

```{r lang.pop}
```
