---
title: "Data_Analyses_MGT_Swabian_single_gender"
author: "Judit Vari"
date: "30 7 2024"
output: html_document
---

```{r setup, include=FALSE}
library (dplyr)
library(broom)
library(tidyverse)
library(corrr)
library(ggcorrplot)
library(car)
library(readr)
library(here)
library(ordinal)
library(lmerTest)
library(emmeans)
library(sjPlot)
library(report)
library (afex)
library(lme4)
library(optimx)
library(sjPlot)
library(ggeffects)
library(factoextra)
library(FactoMineR)
library(RColorBrewer)
library(viridis)
```
### Read data & assign classes
```{r setup1, include=FALSE}
results <- read_delim(here("data_processed", "data_clean.csv"), col_names = TRUE, delim = ",")




as.factor(results$bilendi_id)->results$bilendi_id
as.factor(results$lang.exposure)->results$lang.exposure
as.factor(results$Audio_Track)->results$Audio_Track
as.factor(results$condition)->results$condition
as.factor(results$Speaker)->results$Speaker
as.factor(results$Speaker_Gender)->results$Speaker_Gender
as.factor(results$Attribute)->results$Attribute
as.factor(results$deceived)->results$deceived
as.factor(results$`Political level`)-> results$`Political level`
as.factor(results$Audio_Track_origin_non_st)->results$Audio_Track_origin_non_st
as.factor(results$Audio_Track_origin_st)->results$Audio_Track_origin_st
as.factor(results$Statement_no)-> results$Statement_no
as.factor(results$`identity_lang.variety_non-st`)-> results$`identity_lang.variety_non-st`
as.factor(results$identity_lang.variety_st)-> results$identity_lang.variety_st
as.factor(results$gender)->results$gender
as.factor(results$state_of_residence)->results$state_of_residence
as.factor(results$party)->results$party
as.factor(results$education_school)->results$education_school
as.factor(results$education_profession1)->results$education_profession1
as.factor(results$income)->results$income
as.factor(results$profession)->results$profession
as.factor(results$education_profession1_sum)->results$education_profession1_sum
as.factor(results$education_school_sum)-> results$education_school_sum
as.factor(results$lang.exposure)->results$lang.exposure
as.factor(results$Lang.Variety_Audio)->results$Lang.Variety_Audio




as.numeric(results$Response)->results$Response
as.numeric(results$Att.check_acc)->results$Att.check_acc
as.numeric(results$age)->results$age
as.numeric(results$`proximity_variety_non-st`)->results$`proximity_variety_non-st`
as.numeric(results$proximity_variety_st)->results$proximity_variety_st
as.numeric(results$political_orientation_A)->results$political_orientation_A
as.numeric(results$political_orientation_B)->results$political_orientation_B
as.numeric(results$political_orientation_C)->results$political_orientation_C
as.numeric(results$political_orientation_D)->results$political_orientation_D
as.numeric(results$own_dialect)-> results$own_dialect
as.numeric(results$`social_desirability_A-quantised`)-> results$`social_desirability_A-quantised`
as.numeric(results$`social_desirability_B-quantised`)-> results$`social_desirability_B-quantised`
as.numeric(results$`social_desirability_C-quantised`)-> results$`social_desirability_C-quantised`
as.numeric(results$`social_desirability_D-quantised`)-> results$`social_desirability_D-quantised`
as.numeric(results$`social_desirability_E-quantised`)-> results$`social_desirability_E-quantised`
as.numeric(results$`social_desirability_F-quantised`)-> results$`social_desirability_F-quantised`
as.numeric(results$`social_desirability_G-quantised`)-> results$`social_desirability_G-quantised`
as.numeric(results$`social_desirability_H-quantised`)-> results$`social_desirability_H-quantised`
as.numeric(results$`social_desirability_I-quantised`)-> results$`social_desirability_I-quantised`
as.numeric(results$populism_A)-> results$populism_A
as.numeric(results$populism_B)-> results$populism_B
as.numeric(results$populism_C)-> results$populism_C
as.numeric(results$populism_D)-> results$populism_D
as.numeric(results$political_spectrum)-> results$political_spectrum
```
# scale variables

```{r setup2, include=FALSE}
scale (results$Response)->results$Response
scale(results$political_spectrum)-> results$political_spectrum



scale(results$own_dialect)->results$own_dialect
scale(results$age)->results$age

```
## Create subsets 

### subdived outgroup into two conditions: participants either exposed to only one gender (male or female speaker) or two genders (male vs. female speakers)

### in- and outgroup 
Separate ingroup from outgroup based on exposure to Swabian, outgroup consists of other non-standard, vernacular speakers, standard speakers and bilinguals
Continue with analyses of outgroup data set
```{r setup2, include=FALSE}

results%>%
  filter (condition== "single_gender")->data_all_sing

results%>%
  filter (condition== "contrasted_gender")->data_all_contrast

results%>%
  filter(lang.exposure != "in-group")-> outgroup

data_all_sing%>%
  filter(lang.exposure != "in-group")-> outgroup_sing
data_all_contrast%>%
  filter(lang.exposure != "in-group")-> outgroup_contrast



results%>%
  filter(lang.exposure == "in-group")-> ingroup
data_all_sing%>%
  filter(lang.exposure == "in-group")-> ingroup_sing
outgroup_contrast%>%
  filter(lang.exposure == "in-group")-> ingroup_contrast


# check groups

outgroup%>%
  group_by(lang.exposure)%>%
  summarise(n_distinct(bilendi_id))->lang.ex_out

ingroup%>%
   group_by(lang.exposure)%>%
  summarise(n_distinct(bilendi_id))->lang.ex_in



# Sample Sizes



outgroup_sing%>%
  summarise(n_distinct(bilendi_id))->N_outgroup_sing
outgroup_contrast%>%
  summarise(n_distinct(bilendi_id))->N_outgroup_contrast




```

# exclude participants failing attention checks

```{r setup3, include=FALSE}

outgroup_sing%>%
  ggplot(aes(x=Att.check_acc)) +
  ggtitle ("Plot of Attention Check")+
  xlab("accuracy attention check")+
         geom_density()-> plot_attention

outgroup_sing%>%
  filter(Att.check_acc > 85)%>%
  summarise(n_distinct(bilendi_id))-> pp_above_85atten

outgroup_sing%>%
  filter(Att.check_acc > 85)->outgroup_sing

outgroup_sing%>%
  ggplot(aes(x=Att.check_acc)) +
  ggtitle ("Plot of Attention Check")+
  xlab("accuracy attention check")+
         geom_density()-> plot_attention

plot_attention


```
## Plots raw data
plot responses attributes
```{r plot responses attributes}

# Charisma
outgroup_sing%>%
  filter (Attribute == "charismatisch")%>%
ggplot(aes(x=Response)) +
  ggtitle ("Plot of Attribute Charisma")+
  xlab("ratings")+
         geom_density()-> plot_charisma

plot_charisma


outgroup_sing%>%
  drop_na(Lang.Variety_Audio)%>%
filter (Attribute == "charismatisch")%>%
ggplot(aes(y=Response, x=Lang.Variety_Audio))+
geom_boxplot()+
  ggtitle ("Plot of Attribute Charisma")

## all attributes

outgroup_sing%>%
  drop_na(Lang.Variety_Audio)%>%
ggplot(aes(y=Response, x=Attribute))+
geom_boxplot()+
  ggtitle ("Plot of all Attributes")

```

## Prep political background  
####PCA

```{r PCA_populism, echo=FALSE}
outgroup_sing%>%
  ungroup()%>%
  select(bilendi_id, populism_A, populism_B, populism_C, populism_D)-> PCA_pop_data


distinct (PCA_pop_data)-> PCA_pop_data 
pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE, graph = TRUE) # option to include quali & quanti variables


fviz_eig(pca_pop) # scree plot variance explained dimensions, keep 2

pca_pop$var$coord

pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE,
               graph = T, ncp = 2)

summary(pca_pop)

dimdesc(pca_pop, axes = c(1,2))



p_1a <- fviz_pca_var(pca_pop,geom = c("point","text"),
                  label = "var",
                  repel = TRUE,
                  col.var = "contrib",   # colour active variables according to their contribution to PCA axes
                  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
                  title= "PCA populism"
)

p_1a 

#ggsave(here("Output", "outgroup_PCA_populism.jpg"))
```
*dimension reduction populism scales 1-4 after PCA*
```{r PCA_dim_reduction_populism, echo=FALSE}


populism_dim <- pca_pop$ind$coord [,1]

as_tibble(populism_dim)->populism_dim

bind_cols(PCA_pop_data, populism_dim)->PCA_pop_data_final

left_join (outgroup_sing, PCA_pop_data_final, by = c("bilendi_id", "populism_A", "populism_B", "populism_C", "populism_D"))-> outgroup_sing # 
  
rename (outgroup_sing, populism_dim = value)-> outgroup_sing


# scale

scale (outgroup_sing$populism_dim)-> outgroup_sing$populism_dim
```
*final dummy variables populism*
create 2 dummy variables for populism a) mean of populism scores items A-C, but exclude pop D -> PCA shows very different b) use principal component 1 as dummy
```{r poplitical bckgr pop_dummies, echo=FALSE}
outgroup_sing %>%
  mutate(populism_all = rowMeans(across(c(populism_A, populism_B, populism_C), as.numeric, .names = "mean_{col}"), na.rm = TRUE)) -> outgroup_sing

# scale

scale (outgroup_sing$populism_all)-> outgroup_sing$populism_all


outgroup_sing%>%
  distinct(bilendi_id, populism_all)%>%
ggplot(aes(x=populism_all))+
  ggtitle("Plot of Populism Mean Scores") +
         geom_density()+
  ylab("no. of participants")+
  xlab("total score of populism items 1-3")-> Plot_sum_pop1
Plot_sum_pop1
#ggsave(here("Output", "Plot_sum_pop1.jpg"))


# add new populism dimension 1 of PCA
as.numeric(outgroup_sing$populism_dim)-> outgroup_sing$populism_dim

populism_dim%>%
   ggplot(aes(x=value))+
     ggtitle("Plot of Populism Dimension") +
     geom_density()+
  xlab ("Populism Prinincipal Component Scores")-> Plot_sum_pop2
Plot_sum_pop2

```

# Plot polit. backgr

```{r political_bckgr}


outgroup_sing%>%
  ggplot(aes(x=political_spectrum))+
  ggtitle("Plot of Political Spectrum") +
         geom_density()+
  ylab("no. of participants")+
  xlab("from left to right")-> Plot_polt.spec
Plot_polt.spec


```

# Overview correlations nummeric variables partcipant background & Attributes
```{r corr matrix}
outgroup_sing%>%
  ungroup()%>%
  select(bilendi_id, Response, Attribute, Audio_Track, age, political_spectrum, populism_A, populism_B, populism_C, populism_D, populism_all, own_dialect, populism_dim)-> nummeric

distinct(nummeric)->nummeric

nummeric%>%
  pivot_wider(names_from = Attribute, values_from = Response, id_cols = c("bilendi_id", "Audio_Track", "age", "political_spectrum", "populism_all", "own_dialect"))-> nummeric_long

nummeric_long%>%
distinct()%>%
  select(-bilendi_id, -Audio_Track)%>%
  drop_na()->nummeric_long

nummeric_long %>%
mutate(across(5:10, as.numeric))-> nummeric_long

cor(nummeric_long)->matrix_num_long

matrix_num_long
# Visualize correlations


ggcorrplot(matrix_num_long, 
           title = "Nummeric variables", hc.order = TRUE, 
           type = "lower",lab = TRUE, lab_size = 2,  insig = "blank")->plot_corr_matrix
plot_corr_matrix

#ggsave(here ("output", "plot_corr_matrix.jpg"))
```


```{r PCA personality traits}


nummeric_long

PCA_attribute <- PCA(nummeric_long [, 5:10], scale.unit =TRUE, graph = TRUE) # option to include quali & quanti variables


fviz_eig(PCA_attribute) # scree plot variance explained dimensions, keep 2

PCA_attribute$var$coord

PCA_attribute <- PCA(nummeric_long [, 5:10], scale.unit =TRUE,
               graph = T, ncp = 2)

summary(PCA_attribute)

dimdesc(PCA_attribute, axes = c(1,2))



p_character <- fviz_pca_var(PCA_attribute,geom = c("point","text"),
                  label = "var",
                  repel = TRUE,
                  col.var = "contrib",   # colour active variables according to their contribution to PCA axes
                  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
                  title= "PCA character traits"
)

p_character 

```
# Impact language variety main 
## RQ1: Do outgroup participants rate speakers of standard language variety more charismatic compared the vernacular variety?

Yes: effect of lang.variety on charisma ratings

Effect moderated by own dialect usage: the more dialect usage the less positive Standard German compared to vernacular, but still more positive

But effect not moderated by language exposure


```{r glm_lang.var_chari, eval=FALSE, include=FALSE}


# only charisma ratings
outgroup_sing%>%
  filter(Attribute=="charismatisch")->outgroup_sing_chari


outgroup_sing_chari$Lang.Variety_Audio = relevel(outgroup_sing_chari$Lang.Variety_Audio, ref = "Regional Variety")

# variable own dialect

lmer (Response ~ Lang.Variety_Audio*own_dialect + Statement_no + Speaker + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1_lang.var
summary(model1_lang.var)
anova(model1_lang.var)


# variable language exposure

outgroup_sing_chari$lang.exposure = relevel(outgroup_sing_chari$lang.exposure, ref = "standard_variety ")


lmer (Response ~ Lang.Variety_Audio*lang.exposure + Statement_no + Speaker + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model2_lang.var
summary(model2_lang.var)
anova(model2_lang.var)

# Plots

plot_model(model1_lang.var, title = "Predicted values of charisma ratings", type = "pred", terms = c("own_dialect", "Lang.Variety_Audio"), show.ci = T)+
             ylab ("Charisma ratings")->plot_model1_lang.var
   
plot_model1_lang.var

```

# Moderation Gender
## RQ 2: Does gender moderate an effect of lang. variety?

No:  no effects of gender (pp or speaker) in interaction with lang. variety and no main effects of gender

BUT: 
1.) gender X own_dialect sign.  
=> men are more likely to be dialect speakers and to evaluate speakers more positively (more charismatic) in general compared to women

2.) Lang.Variety_Audio X pp gender approaching. sign. p= 0.06960 in separate 2-way interaction model

```{r glm_lang.var_chari_gender, eval=FALSE, include=FALSE}
# only charisma ratings
outgroup_sing%>%
  filter(Attribute=="charismatisch")->outgroup_sing_chari


outgroup_sing_chari$Lang.Variety_Audio = relevel(outgroup_sing_chari$Lang.Variety_Audio, ref = "Regional Variety")


outgroup_sing_chari%>%
  filter(gender != "Divers")->outgroup_sing_chari
outgroup_sing_chari$gender = relevel(outgroup_sing_chari$gender, ref = "Weiblich")



# lmer (Response ~ Lang.Variety_Audio*Speaker_Gender*gender + Statement_no + Polit_ori +  own_dialect + (Lang.Variety_Audio*Speaker_Gender|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence

#lmer (Response ~ Lang.Variety_Audio*Speaker_Gender*gender + Statement_no + Polit_ori +  own_dialect + (Lang.Variety_Audio+Speaker_Gender|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence

# max model: 4 way interaction
lmer (Response ~ Lang.Variety_Audio*Speaker_Gender*gender*own_dialect + Statement_no + Speaker +  + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> modelMax_gender
summary(modelMax_gender)
anova(modelMax_gender)
vcov(modelMax_gender)

# only 3 way interaction

lmer (Response ~ Lang.Variety_Audio*Speaker_Gender*gender + own_dialect + Statement_no + Speaker +  + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a
summary(model1a)
anova(model1a)


lmer (Response ~ Lang.Variety_Audio*Speaker_Gender*own_dialect  + Statement_no + Speaker +  (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1b
summary(model1b)
anova(model1b)


lmer (Response ~ Lang.Variety_Audio*gender*own_dialect  + Statement_no + Speaker +  + Speaker_Gender +(Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1c
summary(model1c)
anova(model1c)

# Plots 


plot_model(modelMax_gender, title = "Predicted values of charisma ratings", type = "pred", terms = c("Lang.Variety_Audio", "Speaker_Gender", "gender"), show.ci = T)+
             ylab ("Charisma ratings")+
    labs(colour= str_wrap("Speaker Gender", width = 15),  subtitle = "Participant Gender")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))->plot_modelMax_gender
   
plot_modelMax_gender

# Only 2 way interactions

## lang. variety x speaker gender


lmer (Response ~ Lang.Variety_Audio*Speaker_Gender  + Statement_no + Speaker + own_dialect + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model2b
summary(model2b)
anova(model2b)



# lang. variety x pp gender

lmer (Response ~ Lang.Variety_Audio*gender  + Statement_no + Speaker + Speaker_Gender+ own_dialect +(Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model2c
summary(model2c)
anova(model2c)


# speaker gender x pp gender

lmer (Response ~ Speaker_Gender*gender  + Statement_no + Speaker + Lang.Variety_Audio +own_dialect+ (Speaker_Gender|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model2d
summary(model2d)
anova(model2d)

## own_dialect x pp gender

### slope for female
lmer (Response ~ own_dialect*gender  + Statement_no + Speaker + Lang.Variety_Audio + Speaker_Gender + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_dialect_pp_gender
summary(model_dialect_pp_gender)
anova(model_dialect_pp_gender)

### slope for male
outgroup_sing_chari$gender = relevel(outgroup_sing_chari$gender, ref = "Männlich")
lmer (Response ~ own_dialect*gender  + Statement_no + Speaker + Lang.Variety_Audio + Speaker_Gender + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_dialect_pp_gender
summary(model_dialect_pp_gender)
anova(model_dialect_pp_gender)


# Plot

plot_model(model1c, title = "Predicted values of charisma ratings", type = "pred", 
                           terms = c("own_dialect", "gender"), show.ci = TRUE) +
                ylab("Charisma ratings") +
                labs(colour = str_wrap("Participant gender", width = 15)) +
                theme(axis.text.x = element_text(angle = 45, hjust = 1))-> plot_model1c

plot_model1c

plot_model(model1b, title = "Predicted values of charisma ratings", type = "pred", terms = c("own_dialect", "Lang.Variety_Audio", "Speaker_Gender"), show.ci = T)+
             ylab ("Charisma ratings")+
    labs(colour= str_wrap("Speaker Gender", width = 15))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))->plot_model1b
   
plot_model1b

plot_model(model_dialect_pp_gender, title = "Predicted values of charisma ratings", type = "pred", terms = c("own_dialect", "gender"), show.ci = T)+
             ylab ("Charisma ratings") ->plot_model_dialect_pp_gender
plot_model_dialect_pp_gender

```
# RQ 2: Does pop. attitude moderate an effect of lang. variety?

main effect of populism. the more populist attitudes the more pos. rating of speakers in general

interaction between lang. variety x populism dimension x own dialect usage

interaction stimuli political orientation & pop. attitude pp -> the more populist attitudes the more positive ratings of statements with right orientation

```{r lang_var & pop}

## Populism measure means of 3 different scales

lmer (Response ~ Lang.Variety_Audio*populism_all*own_dialect + gender + age + education_school_sum + political_spectrum + Polit_ori +  (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1poli 
summary(model1poli)
anova(model1poli)

## Populism measure dimension reduction

outgroup_sing_chari$Lang.Variety_Audio = relevel(outgroup_sing_chari$Lang.Variety_Audio, ref = "Regional Variety")

# slope of Lang.Variety = Regional #1.340e-01
lmer (Response ~ Lang.Variety_Audio*populism_dim*own_dialect + gender + age + education_school_sum + political_spectrum + Polit_ori +  (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model2polia 
summary(model2polia)

# slope of populism for level Lang.Variety = Standard #  1.549e-01
outgroup_sing_chari$Lang.Variety_Audio = relevel(outgroup_sing_chari$Lang.Variety_Audio, ref = "Standard German")

lmer (Response ~ Lang.Variety_Audio*populism_dim*own_dialect + gender + age + education_school_sum + political_spectrum + Polit_ori +  (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model2polib
summary(model2polib)
anova(model2polib)

plot_model(model2polib, title = "Predicted values of charisma ratings", type = "pred", terms= c("own_dialect",  "Lang.Variety_Audio",  "populism_dim"), show.ci = T)+
             ylab ("Charisma ratings")->plot_model2polib
   
plot_model2polib

## interaction stimuli political orientation & pop. attitude pp

lmer (Response ~ Lang.Variety_Audio*populism_dim*Polit_ori  + gender + age + education_school_sum + political_spectrum +(Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model3poli 
summary(model3poli)
anova(model3poli)

plot_model(model3poli, title = "Predicted values of charisma ratings", type = "pred", terms= c("populism_dim", "Polit_ori"), show.ci = T)+
             ylab ("Charisma ratings")->plot_model3poli
   
plot_model3poli

# populism & gender

lmer (Response ~ Lang.Variety_Audio*populism_dim*gender + age + education_school_sum + own_dialect + political_spectrum + Polit_ori +  (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_pop_gender
summary(model_pop_gender)
anova(model_pop_gender)

plot_model(model1polid, title = "Predicted values of charisma ratings", type = "pred", terms= c("populism_dim", "gender"), show.ci = T)+
             ylab ("Charisma ratings")->plot_model_pop_gender
   
plot_model_pop_gender


```
# RQ 3: Does political backgr moderate an effect of lang. variety?
```{r lang.pol_bckgr}
# general backr: populism & party

glmer ( party ~ political_spectrum  + gender + age + education_school_sum + populism_dim + own_dialect + (1|bilendi_id), data = outgroup_sing_chari, family = "binomial") -> model_poli_bckgr
summary(model_poli_bckgr) # takes 5 min, fails to converge
anova(model_poli_bckgr)

plot_model(model3poli, title = "Predicted values of charisma ratings", type = "pred", terms= c("populism_dim", "Polit_ori"), show.ci = T)+
             ylab ("Charisma ratings")->plot_model_poli_bckgr
```
# RQ: 4: Does SES moderate the effect of lang. variety on charisma ratings?

```{r lang_SES}
lmer (Response ~ Lang.Variety_Audio*own_dialect*education_school_sum + Statement_no + Speaker + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_lang.var_edu1
summary(model_lang.var_edu1)
anova(model_lang.var_edu1) # sig. interaction: own_dialect*education_school_sum + education_school_sum main effect approach sign.

lmer (Response ~ Lang.Variety_Audio*own_dialect*education_school + Statement_no + Speaker + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_lang.var_edu2
summary(model_lang.var_edu2) # own_dialect:education_school  approach sing.
anova(model_lang.var_edu2)

lmer (Response ~ Lang.Variety_Audio*own_dialect*education_profession1 + Statement_no + Speaker + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_lang.var_edu3
summary(model_lang.var_edu3) 
anova(model_lang.var_edu3)#  Lang.Variety_Audio:own_dialect:education_profession1 approach sign

lmer (Response ~ Lang.Variety_Audio*own_dialect*education_profession1_sum + Statement_no + Speaker + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_lang.var_edu4
summary(model_lang.var_edu4) 
anova(model_lang.var_edu4) # own_dialect:education_profession1_sum                    sign.

# Income

levels(outgroup_sing_chari$income)

outgroup_sing_chari%>%
  filter(income != "Ich möchte die Frage nicht beantworten" & income !=
                                                "Ich weiß nicht")->outgroup_sing_chari_income
  


outgroup_sing_chari_income$income <- factor(outgroup_sing_chari_income$income, 
                                     levels = c("10000 Euro und mehr", 
                                                "7500 bis unter 10000 Euro", 
                                                "5000 bis unter 7500 Euro", 
                                                "4000 bis unter 5000 Euro", 
                                                "3000 bis unter 4000 Euro", 
                                                "2500 bis unter 3000 Euro", 
                                                "2000 bis unter 2500 Euro", 
                                                "1500 bis unter 2000 Euro", 
                                                "1250 bis unter 1500 Euro", 
                                                "1000 bis unter 1250 Euro", 
                                                "500 bis unter 750 Euro", 
                                                "750 bis unter 1000 Euro", 
                                                "Unter 500 Euro"))


lmer (Response ~ Lang.Variety_Audio*own_dialect*income + Statement_no + Speaker + (Lang.Variety_Audio|bilendi_id) +  (1|Audio_Track), data = outgroup_sing_chari_income,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_lang.var_edu5
summary(model_lang.var_edu5) 
anova(model_lang.var_edu5)# own_dialect:income sign.

# plots

plot_model(model_lang.var_edu5,title = "Predicted values of charisma ratings", type = "pred", terms = c("own_dialect", "income"), show.ci = TRUE) +
  ylab("Charisma ratings") +
  labs(colour = str_wrap("dialect", width = 15)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_color_brewer(palette = "Set4")->plot_model_lang.var_edu5
plot_model_lang.var_edu5



plot_model(model_lang.var_edu4, title = "Predicted values of charisma ratings", type = "pred", terms= c("own_dialect", "education_profession1_sum"),show.ci = T)+
             ylab ("Charisma ratings")+
  labs(colour= str_wrap("tertiary education", width = 15))->plot_model_lang.var_edu4

plot_model_lang.var_edu4

plot_model(model_lang.var_edu1, title = "Predicted values of charisma ratings", type = "pred", terms= c("own_dialect", "education_school_sum"),show.ci = T)+
             ylab ("Charisma ratings")+
  labs(colour= str_wrap("secondary education", width = 15))->plot_model_lang.var_edu1

plot_model_lang.var_edu1
```
# Participant descriptives

```{r pp descriptives}




## check: participant background

### federal state

outgroup_sing_chari%>%
  group_by(state_of_residence)%>%
  summarise(n_distinct(bilendi_id))->pp_state

### participant age

outgroup_sing_chari%>%
  ungroup()%>%
  drop_na(age)%>%
  summarise(mean(age), sd(age), min (age), max (age))->pp_age

### participant gender

outgroup_sing_chari%>%
  group_by(gender)%>%
  summarise(n_distinct(bilendi_id))->pp_gender_outgroup

resultss%>%
  group_by(gender)%>%
  summarise(n_distinct(bilendi_id))->pp_gender_all


### sum_education_school
outgroup_sing_chari%>%
  ungroup()%>%
  group_by(education_school_sum)%>%
  summarise(n_distinct(bilendi_id))->sum_education

### sum_profession
outgroup_sing_chari%>%
  group_by(education_profession1_sum)%>%
  summarise(n_distinct(bilendi_id))->sum_profession1


### income

outgroup_sing_chari%>%
  group_by(income)%>%
  summarise(n_distinct(bilendi_id))->income

### profession

outgroup_sing_chari%>%
  group_by(profession)%>%
  summarise(n_distinct(bilendi_id))->sum_profession

# language

outgroup_sing_chari%>%
  group_by(lang.exposure)%>%
  summarise(n_distinct(bilendi_id))->sum_lang.exposure

outgroup_sing_chari%>%
  ungroup()%>%
    drop_na(own_dialect)%>%
  summarise(mean(own_dialect), sd (own_dialect), min (own_dialect), max(own_dialect))->own_lang.variety 

# party

outgroup_sing_chari%>%
  group_by(party)%>%
  summarise(n_distinct(bilendi_id))->sum_party


## check randomization:

outgroup_sing_chari%>%
  group_by(`randomiser-rtb5`,`counterbalance-nimi`, `counterbalance-x3xi`, `counterbalance-xq3l`)%>%
  summarise(n_distinct(bilendi_id))->random
```

